Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-06 manuscript.tex
minor updates

\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density
\thanks{Based on observations collected at the La Silla Parana Observatory,
ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}

@@

In this Section we present the analysis conducted on the star Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec. \ref{sec:3} with the usual approach based on fitting a Normal density for estimating the RV and asymmetry of the CCF. 
%to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN. 
Four other stars have been analyzed with the proposed method and details can be found in Appendix \ref{appendix}. 
For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a SNR at 550 nm of 10 were selected.

>>>>

\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory,
ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}

@@

In this Section we present the analysis conducted on the star Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec. \ref{sec:3} with the usual approach based on fitting a Normal density for estimating the RV and asymmetry of the CCF. 
%to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN. 
Four other stars have been analyzed with the proposed method and details can be found in Appendix \ref{appendix}. 
For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a SNR of 10 at 550 nm were selected.
